---
title: "p8105_hw1_yd2868"
output: github_document
date: "2025-09-16"
---
Load needed packs.
```{r}
library(moderndive)
library(tidyverse)
```

# problem1
Load dataset
```{r}
data("early_january_weather")
```

#### Description of the dataset

This dataset is hourly meteorological data for LGA, JFK and EWR for the month of January 2013. 

The variables are "origin"(Weather station,which is EWR); "year", "month", "day", "hour"(Time of recording); "temp", "dewp"(Temperature and dewpoint in F); "humid(Relative humidity)"; "wind_dir", "wind_speed", "wind_gust"(Wind direction  in degrees, speed and gust speed in mph); "precip"(Precipitation, in inches); "pressure"(Sea level pressure in millibars); "visib"(Visibility in miles); "time_hour"(Date and hour of the recording as a POSIXct date).

This dataset has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 

The mean temperature is `r mean(early_january_weather$temp)`.

#### Scatterplot of temp vs time_hour
Draw and save the scatterplot
```{r}
ggplot(data = early_january_weather , mapping = aes(y = temp , x = time_hour , color = humid)) + geom_point()
ggsave("temp_vs_time_hour.png", path = "C:\\Users\\a1249\\OneDrive\\Desktop\\R homework\\p8105_hw1_yd2868")
```

# Problem2

Create the data frame
```{r}
num = rnorm(10, mean = 0, sd = 1)
df = tibble(
  number = num,
  logical = num > 0,
  character = c("a","b","c","d","e","f","g","h","i","j"),
  factor = factor(c("A","B","C","A","A","C","B","A","C","B"))
)
```

take the mean of each variable
```{r}
mean(pull(df,1))
mean(pull(df,2))
mean(pull(df,3))
mean(pull(df,4))
```

apply as.numeric to three vectors
```{r,eval=FALSE}
as.numeric(pull(df,2))
as.numeric(pull(df,3))
as.numeric(pull(df,4))
```
we can convert logical and factor variables to numeric variables, but character variables do not have a natural numerical correspondence.

TRUE is converted to 1, while FALSE is converted to 0. This is why we can compute the mean of a logical vector.

Factor variables are internally stored as integer codes representing their levels, so converting them to numeric gives these integer codes. By contrast, characters themselves do not have a natural numeric correspondence, so attempting to convert them results in NA, and thus taking the mean of a character vector is not possible.
